PyQBench: a Python library for benchmarking gate-based quantum computers

### 2023-07-12 reviews/softwarex/reviews_1/response/response.tex

\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}

\newcommand{\1}{{\rm 1\hspace{-0.9mm}l}}

\newenvironment{response}{\vspace{1em}\noindent\textbf{Response}}{\vspace{1em}}

\begin{document}
We would like to thank the reviewers for their comments. Below we provide
a response to their specific remarks.

\section{Reviewer 1}

\begin{enumerate}

  \item The generalization of the suggested benchmarking technique to multiple qubits should be described in more detail, 
        explicitly mentioning whether the complexity of the derivation and actual benchmarking depends on the number of 
        qubits.

  \begin{response}
  We thank the referee for this suggestion. We extended the manuscript with a paragraph describing differences between
  a single--qubit and higher-dimensional cases.

\end{enumerate}
\section{Reviewer 2}

\end{document}

### 2023-08-18 txt/manuscript_short.tex
cross-netropy

@@

Without loss of generality\footnote{Explaining why we can consider only discrimination scheme
between $\PP_{\Id}$ and $\PP_{U}$ is beyond the scope of this paper. See
\cite{puchala2018strategies} for a in depth explanation.}, we consider discrimination task between
single qubit measurements $\PP_\Id$, performed in the computational Z-basis, and an alternative
measurement $\PP_U$ performed in the basis $U$. 
The discrimination scheme presented in Fig.~\ref{fig:theoretical_scheme} requires an
auxiliary qubit. First, the joint system is prepared in some state $\ket{\psi_0}$. Then, one of the
measurements, either $\PP_U$ or $\PP_\1$, is performed on the first part of the system. Based on its
outcome $i$, we choose another binary measurement $\mathcal{P}_{V_i}$ and perform it on the second qubit,
obtaining the outcome $j$. Finally, if $j=0$, we say that the performed measurement is
$\mathcal{P}_U$, otherwise we say that it was $\mathcal{P}_\Id$.

Note, however, that the discrimination scheme described above can work regardless of dimensionality 
of the unitary $U$. The main difference is the dimension of the auxiliary system, which in general
can be larger than two. This dimension depends on the Schmidt rank of the optimal input state. However, 
for most discrimination schemes, the  Schmidt rank equals at most two, and hence the auxiliary system
is also a qubit, see \cite{puchala2018strategies} for details. Note that the final measurement $\PP_{V_i}$ 
is always binary, independently of the dimension of auxiliary system.

Naturally, we need to repeat the
same procedure multiple times for both measurements to obtain a reliable estimate of the underlying
probability distribution. In PyQBench, we assume that the experiment is repeated the same number of
times for both $\PP_U$ and $\PP_\Id$.

>>>>

Finally, we should mention cross-entropy
benchmarking~\cite{boixo2018characterizing}, which was utlilized in validation
of the Sycamore-53 QPU supremacy experiments~\cite{arute2019quantum}. In this
approach, the quality of an algorithm implemented on the QPU is measured by
calculating the cross entropy of bit-strings actually sampled from the QPU,
compared to ideal bitstrings.

@@

Without loss of generality\footnote{Explaining why we can consider only discrimination scheme
between $\PP_{\Id}$ and $\PP_{U}$ is beyond the scope of this paper. See
\cite{puchala2018strategies} for a in depth explanation.}, we consider discrimination task between
single qubit measurements $\PP_\Id$, performed in the computational Z-basis, and an alternative
measurement $\PP_U$ performed in the basis $U$. Note, however, that the discrimination scheme
described below can work regardless of dimensionality of the system, see
\cite{puchala2018strategies} for details.

The discrimination scheme presented in Fig.~\ref{fig:theoretical_scheme} requires an
auxiliary qubit. First, the joint system is prepared in some state $\ket{\psi_0}$. Then, one of the
measurements, either $\PP_U$ or $\PP_\1$, is performed on the first part of the system. Based on its
outcome $i$, we choose another measurement $\mathcal{P}_{V_i}$ and perform it on the second qubit,
obtaining the outcome $j$. Finally, if $j=0$, we say that the performed measurement is
$\mathcal{P}_U$, otherwise we say that it was $\mathcal{P}_\Id$. Naturally, we need to repeat the
same procedure multiple times for both measurements to obtain a reliable estimate of the underlying
probability distribution. In PyQBench, we assume that the experiment is repeated the same number of
times for both $\PP_U$ and $\PP_\Id$.
